### 2018-08-15 Sections/network_topologies.tex
floats

Fig.~\ref{fig:complete_graph} illustrates the $K_{15}$ graph. The number of edges scales as $O(n^2)$. Clearly route-finding is trivial, since there is always a direct link from sender to receiver, with no possibility of collisions with other packets, requiring $O(1)$ search time (assuming all users are communicating only via their direct links with one another, which may not strictly be the case when costs are factored into strategies).

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{K_15}
\caption{The 15-vertex complete graph, $K_{15}$. Every vertex has an edge to every other, with a total of 105 edges.} \label{fig:complete_graph}
\end{figure}

@@

A lattice graph is simply an \mbox{$n\times m$} lattice of vertices (of any geometry, e.g squares), connecting each vertex to its immediate geometric neighbours. This type of graph is useful when link costs are measured in terms of Euclidean distances, and nodes have nearest neighbour links. An example is shown in Fig.~\ref{fig:lattice}.

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{lattice}
\caption{A \mbox{$10\times 11$} square lattice graph, and how it might represent a network topology with geographically associated costs. Notice that Hobart has no internet connection (why even include Tasmania at all?).} \label{fig:lattice}
\end{figure}

@@

In the case of a balanced lattice, in which all edges are of equal weight, the cost of a route is the sum of the number of steps in the vertical and horizontal directions, also known as the Manhattan or $L_1$ distance,
\begin{align}
L_1 = |x_\mathrm{start} - x_\mathrm{finish}| + |y_\mathrm{start} - y_\mathrm{finish}|.
\end{align}
In this case, route finding is simplified, since \textit{all} routes, which strictly traverse in one direction vertically and one direction horizontally, are optimal and of equal distance. Thus, the maximum number of hops between any two points in the network is \mbox{$O(m+n)$}.

@@

A tree is a graph containing no cycles, only \textit{branches}. There are many uses for tree graphs, but one property is of particular convenience in many applications: because the graph is acyclic, there is always exactly one path from any vertex to any other. This mitigates the need for shortest-path algorithms designed for general graphs, and simplifies route-finding algorithms (to be discussed in Sec.~\ref{sec:path_exp}). However, this brings with it the drawback that the topology is most vulnerable to link failures, since the removal of any link from the tree will separate it into a bipartite graph, making communication between the two disjoint subgraphs (which are also trees) impossible, as there are no redundant routes. In a sense, tree graphs can be considered the polar opposites of complete graphs.

@@

The \textit{depth} ($d$) of a tree is the maximum number of steps from the root node to a terminating node with no children. The depth scales between \mbox{$d=O(|V|)$}, for the trivial linear tree (\mbox{$b_i=1$}), and \mbox{$d=O(\mathrm{log}|V|)$} for non-trivial branching parameters (i.e \mbox{$b_i\neq 1$}).

The worst-case number of edges that must be traversed to reach any vertex from any other is \mbox{$2d=O(\mathrm{log}|V|)$}, which implies that accumulated cost metrics scale as \mbox{$c=O(\mathrm{log}|V|)$}. Trees are the most frugal graphs in their number of edges, which are fixed at \mbox{$|E|=|V|-1$}, irrespective of the branching parameters, since because the graph is strictly acyclic, every addition of an edge requires the addition of exactly a single vertex. This makes tree graphs the cheapest to construct in terms of physical resource usage.

@@

\begin{figure*}[!htb]
\includegraphics[width=0.325\textwidth]{tree_3_8}
\includegraphics[width=0.325\textwidth]{tree_4_8}
\includegraphics[width=0.325\textwidth]{tree_5_8}
\caption{Balanced tree graphs with branching factor $b=8$, and depths $d=3,4,5$. Despite having no redundant paths, the hierarchical structure of balanced trees somewhat resembles that of real-world networks, which are typically decomposed into a pyramid scheme of progressively smaller subnetworks.} \label{fig:tree_example}
\end{figure*}

@@

\begin{figure*}[!htb]
\includegraphics[width=0.47\textwidth]{random_tree_1}
\includegraphics[width=0.47\textwidth]{random_tree_2}
\caption{Random trees with different randomised branching parameters (higher $b$ on the right). When a node has zero branches, it terminates the branch. This type of graph topology qualitatively captures the hierarchical, yet ad hoc qualities of many real-world networks, and may act as a useful test model for simulations.} \label{fig:random_tree}
\end{figure*}

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{MST}
\caption{A random graph (blue) with an MST highlighted (red).} \label{fig:mst}
\end{figure}

@@

\subsection{Percolation}\index{Percolation graph}

A variation on any graph, $G$, is to instead have a randomised implementation of it, whereby each of the possible edges \mbox{$e\in E$} or vertices \mbox{$v\in V$} occurs with some probability \mbox{$0\leq p_\mathrm{perc}\leq 1$}. These are referred to as \textit{edge percolation} and \textit{site percolation} graphs respectively. For any given graph, its associated percolation graph has average vertex and edge counts,
\begin{align}
|E|_\mathrm{av} &= p_\mathrm{edge}\cdot |E|,\nonumber\\
|V|_\mathrm{av} &= p_\mathrm{vertex}\cdot |V|,
\end{align}
for edge and vertex percolations respectively.

Adjusting $p_\mathrm{perc}$ allows us to tune between the desired graph (when $p_\mathrm{perc}=1$) and the completely disconnected graph (when $p_\mathrm{perc}=0$). This model is very useful in real-world applications, allowing unreliable channels/nodes to be incorporated into our network model. The analysis of such percolation networks is invaluable for understanding the robustness of such networks to channel and node failures.

Note that percolation graphs might be disjoint with sufficient defects, in which case the respective network becomes unreliable. Specifically, with sufficiently low $p_\mathrm{perc}$, `islands' may form in the network topology -- small segregated networks, which are unable to interface with the remainder of the network.

For asymptotically large percolation graphs, \textit{percolation theory}\index{Percolation theory} \cite{???} provides thresholds for $p_\mathrm{perc}$ such that routes across the network exist \cite{???}.

Fig.~\ref{fig:perc_graph} illustrates several graphs with different percolation probabilities, and how the larger network segregates into smaller islands as failure rates increase.

\begin{figure*}[!htb]
\includegraphics[width=0.325\textwidth]{random_0}
\includegraphics[width=0.325\textwidth]{random_05}
\includegraphics[width=0.325\textwidth]{random_1}\\
\includegraphics[width=0.325\textwidth]{percolation_1}
\includegraphics[width=0.325\textwidth]{percolation_2}
\includegraphics[width=0.325\textwidth]{percolation_3}
\caption{(top) The 15-vertex randomly-connected percolation graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (top to bottom). (bottom) A square lattice graph subject to different percolation rates (node defects). As the failure rate increases, the larger network segregates into smaller disjoint islands (denoted by colour).} \label{fig:perc_graph}
\end{figure*}

@@

@@

Of course, all the topological structures described until now are in-principle constructs. Of most relevance is the \textit{Web-graph}, the graph of the actual internet (or some other real-world network). Fig.~\ref{fig:webgraph} illustrates some example web-graphs. The combination of random, densely and sparsely connected, and tree structures, and its clear hierarchy are all evident. This encourages our intuition of the different types of structures present in realistic networks.

\begin{figure*}[!htb]
\includegraphics[width=0.481\textwidth]{webgraph_1}
\includegraphics[width=0.47\textwidth]{webgraph_2}
\caption{Examples of real-world web-graphs of the internet, capturing their high-level random tree-like structure. Graphics attributed to the Center for Applied Internet Data Analysis (CAIDA), \texttt{\href{http://www.caida.org}{http://www.caida.org}}.} \label{fig:webgraph}
\end{figure*}

\subsection{Scale-free networks}

\comment{To do}

>>>>

Fig.~\ref{fig:complete_graph} illustrates the $K_{15}$ graph. The number of edges scales as $O(n^2)$. Clearly route-finding is trivial, since there is always a direct P2P link from sender to receiver, with no possibility of collisions with other packets, requiring $O(1)$ search time (assuming all users are communicating only via their direct links with one another, which may not strictly be the case when costs are factored into strategies).

\begin{figure}[htpb]
\includegraphics[width=0.35\textwidth]{K_15}
\caption{The 15-vertex complete graph, $K_{15}$. Every vertex has an edge to every other, with a total of 105 edges.} \label{fig:complete_graph}
\end{figure}

@@

A lattice graph is simply an \mbox{$n\times m$} lattice of vertices (of any geometry, e.g squares), connecting each vertex to its immediate geometric neighbours. The number of edges scales obviously as \mbox{$|E|=O(mn)$}. This type of graph is useful when link costs are measured in terms of Euclidean distances, and nodes have nearest neighbour links, as per Fig.~\ref{fig:lattice}.

\begin{figure}[htpb]
\includegraphics[width=0.35\textwidth]{lattice}
\caption{A \mbox{$10\times 11$} square lattice graph, and how it might represent a network topology with geographically associated costs. Notice that Hobart has no internet connection (why even include Tasmania at all?).} \label{fig:lattice}
\end{figure}

@@

In the case of a balanced lattice, in which all edges are of equal weight, the cost of a route is the sum of the number of steps in the vertical and horizontal directions, also known as the Manhattan or $L_1$ distance,
\begin{align}
L_1 = |x_\mathrm{start} - x_\mathrm{finish}| + |y_\mathrm{start} - y_\mathrm{finish}|.
\end{align}
In this case, route finding is simplified, since \textit{all} routes, which strictly traverse in one direction vertically and one direction horizontally, are optimal and of equal distance. Thus, the diameter (maximum number of hops between any two points) on the network is \mbox{$d=O(m+n)$}.

@@

A tree is a graph containing no cycles, only \textit{branches}\index{Branches}. There are many uses for tree graphs, but one property is of particular convenience in many applications: because the graph is acyclic, there is always exactly one path from any vertex to any other. This mitigates the need for shortest-path algorithms designed for general graphs, and simplifies route-finding algorithms (to be discussed in Sec.~\ref{sec:path_exp}). However, this brings with it the drawback that the topology is most vulnerable to link failures, since the removal of any link from the tree will separate it into a multipartite graph\index{Multipartite graphs}, making communication between the disjoint subgraphs (which are also trees) impossible, as there are no redundant routes. In a sense, tree graphs can be considered the polar opposites of complete graphs.

@@

The \textit{depth} ($d$) of a tree is the maximum number of steps from the root node to a terminating node with no children. The depth scales between \mbox{$d=O(|V|)$}, for the trivial linear tree (\mbox{$b_i=1$}), and \mbox{$d=O(\log |V|)$} for non-trivial branching parameters (\mbox{$b_i\neq 1$}).

The worst-case number of edges that must be traversed to reach any vertex from any other is \mbox{$2d=O(\log|V|)$}, which implies that accumulated cost metrics scale as \mbox{$c=O(\log |V|)$}. Trees are the most frugal graphs in their number of edges, which are fixed at \mbox{$|E|=|V|-1$}, irrespective of the branching parameters, since because the graph is strictly acyclic, every addition of an edge requires the addition of exactly a single vertex. This makes tree graphs the cheapest to construct in terms of physical resource usage.

@@

\begin{figure*}[htpb]
\includegraphics[width=0.325\textwidth]{tree_3_8}
\includegraphics[width=0.325\textwidth]{tree_4_8}
\includegraphics[width=0.325\textwidth]{tree_5_8}
\caption{Balanced tree graphs with branching factor $b=8$, and depths $d=3,4,5$. Despite having no redundant paths, the hierarchical structure of balanced trees somewhat resembles that of real-world networks, which are typically decomposed into a pyramid scheme of progressively smaller subnetworks.} \label{fig:tree_example}
\end{figure*}

@@

\begin{figure*}[htpb]
\includegraphics[width=0.47\textwidth]{random_tree_1}
\includegraphics[width=0.47\textwidth]{random_tree_2}
\caption{Random trees with different randomised branching parameters (higher $b$ on the right). When a node has zero branches, it terminates the branch. This type of graph topology qualitatively captures the hierarchical, yet ad hoc qualities of many real-world networks, and may act as a useful test model for simulations.} \label{fig:random_tree}
\end{figure*}

@@

\begin{figure}[htpb]
\includegraphics[width=0.4\textwidth]{MST}
\caption{A random graph (blue) with an MST highlighted (red).} \label{fig:mst}
\end{figure}

@@

\subsection{Percolation}\index{Percolation topologies}\label{sec:perc_topol}

A variation on any graph is to instead have a randomised implementation of it, whereby each of the possible edges or vertices occur with some probability, $p_\mathrm{edge}$ or $p_\mathrm{vertex}$, otherwise deleted. These are referred to as \textit{edge percolation} and \textit{site percolation} graphs respectively.

For any given graph, its associated percolation graph has average vertex and edge counts,
\begin{align}
|E|_\mathrm{av} &= p_\mathrm{edge}\cdot |E|,\nonumber\\
|V|_\mathrm{av} &= p_\mathrm{vertex}\cdot |V|.
\end{align}

Adjusting $p_\mathrm{edge/vertex}$ allows us to tune between the desired graph $G$ (when $p_\mathrm{edge/vertex}=1$) and the completely disconnected graph (when $p_\mathrm{edge/vertex}=0$).

This model is very useful in real-world applications, allowing unreliable channels/nodes to be incorporated into our network model. The analysis of such percolation networks is invaluable for understanding the robustness of such networks to channel and node failures.

Note that percolation graphs might be disjoint with sufficient defects, in which case the respective network becomes unreliable. Specifically, with sufficiently low $p_\mathrm{edge/vertex}$, `islands' may form in the network topology -- small segregated networks, which are unable to interface with the remainder of the network.

For asymptotically large percolation graphs, \textit{percolation theory}\index{Percolation theory} \cite{???} provides thresholds for $p_\mathrm{edge/vertex}$ such that routes across the network exist in asymptotic limits \cite{???}.

Fig.~\ref{fig:perc_graph} illustrates several square lattice graphs with different percolation probabilities, and how the larger network segregates into smaller disconnected islands as failure rates increase.

\begin{figure*}[htpb]
\includegraphics[width=0.325\textwidth]{percolation_1}
\includegraphics[width=0.325\textwidth]{percolation_2}
\includegraphics[width=0.325\textwidth]{percolation_3}
\caption{A square lattice graph subject to different percolation rates (node defects). As the failure rate increases, the larger network segregates into a multipartite graph of smaller disjoint islands (denoted by colour).} \label{fig:perc_graph}\index{Percolation topologies}
\end{figure*}

%
% Random
%

\subsection{Random}\index{Random topologies}

We refer to a random graph as being one in which edges between each pair of vertices occur with some probability $p_\mathrm{edge}$. No vertices are removed from the network, although some may have order \mbox{$|v|=0$}, i.e \mbox{$p_\mathrm{vertex}=1$}. This can be thought of as the edge percolation graph of the complete graph $K_{|V|}$. Some examples are shown in Fig.~\ref{fig:random_graph}.

\begin{figure*}[htpb]
\includegraphics[width=0.325\textwidth]{random_0}
\includegraphics[width=0.325\textwidth]{random_05}
\includegraphics[width=0.325\textwidth]{random_1}
\caption{The 15-vertex random graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (left to right).} \label{fig:random_graph}\index{Random topologies}
\end{figure*}

@@

\subsection{Scale-free networks}\index{Scale-free networks}\label{sec:scale_free_networks}

Scale-free networks are not defined as obeying a specific topological structure, but rather as following a particular statistical distribution in the connectedness of their nodes. Specifically, the probability distribution function\index{Probability distribution function} for the order of vertices roughly follows a Pareto distribution or power law\index{Power law},
\begin{align}\label{eq:pareto_dist}
	P(k) \sim k^{-\gamma},
\end{align}
where $P(k)$ is the probability of a vertex having order $k$ (up to normalisation), and \mbox{$\gamma>1$}. Most commonly \mbox{$2\leq\gamma\leq 3$}. Fig.~\ref{fig:power_law} illustrates this scaling behaviour for different power coefficients.

\begin{figure}[htpb]
\includegraphics[width=0.475\textwidth]{power_law}
\caption{Examples of the power law, characteristic of the vertex order distribution in scale-free networks.}\label{fig:power_law}\index{Scale-free networks}\index{Power law}	
\end{figure}

This distribution is observed empirically in many real-world networks, and as such is more an observation about the typical behaviour of naturally occurring and evolving human-made networks than an explicit definition for their construction. However, owing to this particular statistical behaviour, and the underlying causations for their Pareto distribution, much has been researched and is known about the properties of scale-free networks.

One notable characteristic is their hierarchical structure, with a small number of very highly-connected `hubs'\index{Hubs} at the top of the food chain, which quickly connect onto smaller hubs, and so on down the food chain with decreasing connectivity.

A feature of scale-free networks of especial interest in the context of computer networks is their robustness against node failure. Suppose we constructed a percolated (Sec.~\ref{sec:perc_topol}) instance of a typical scale-free network. Such a network is highly robust against node/edge deletions compared to many other graph constructions, in the sense that a relatively large number of failures must occur to disconnect the graph. This makes the scale-free network characteristic a particularly attractive one from the perspective of the failure-tolerance of the network.

Scale-free networks typically exhibit extremely small diameter (average distance between nodes), scaling as \cite{bib:PhysRevLett.90.058701},
\begin{align}
	d = O(\log(\log |V|)).
\end{align}
That is, they exhibit (exponentially) smaller diameter than tree graphs (which already exhibit only logarithmic depth). Thus, expanding the network (in a manner consistent with the model) by adding a moderate number of new nodes effectively leaves graph diameter unchanged -- the graph diameter is virtually a constant under modest evolution.

@@

Of course, all the topological structures described until now are in-principle constructs. Of most relevance is the \textit{internet web-graph}, the graph of the actual internet (or some other real-world network).

Fig.~\ref{fig:webgraph} illustrates some example web-graphs, constructed from subsets of data from the actual internet. The combination of random, densely and sparsely connected, and tree structures, and its clear hierarchy are all evident. This encourages our intuition of the different types of structures present in realistic networks.

\begin{figure*}[htpb]
\includegraphics[width=0.481\textwidth]{webgraph_1}
\includegraphics[width=0.47\textwidth]{webgraph_2}
\caption{Examples of real-world web-graphs of the internet, capturing their high-level random tree-like structure. Graphics attributed to the Center for Applied Internet Data Analysis (CAIDA), \texttt{\href{http://www.caida.org}{http://www.caida.org}}.}\index{Internet web-graph} \label{fig:webgraph}
\end{figure*}

The internet web-graph has been observed to be a scale-free network (Sec.~\ref{sec:scale_free_networks}), observing its power law distribution in node connectivity, as per Eq.~(\ref{eq:pareto_dist}).

### 2018-08-15 Sections/optical_encoding_of_quantum_information.tex

\subsubsection{Transverse electro-magnetic modes}\index{Transverse electro-magnetic modes}

@@

\begin{figure*}[htpb]
\includegraphics[width=0.49\textwidth]{TEM_cylinder}
\includegraphics[width=0.49\textwidth]{TEM_rectangular}
\caption{TEM$_{mn}$ modes for cylindrical (left) and rectangular (right) mode profiles.}\index{Transverse electro-magnetic modes}\label{fig:TEM_modes}
\end{figure*}

>>>>

\subsubsection{Transverse electro-magnetic modes}\index{Transverse electro-magnetic (TEM) modes}

@@

\begin{figure*}[htpb]
\includegraphics[width=0.49\textwidth]{TEM_cylinder}
\includegraphics[width=0.49\textwidth]{TEM_rectangular}
\caption{TEM$_{mn}$ modes for cylindrical (left) and rectangular (right) mode profiles.}\index{Transverse electro-magnetic (TEM) modes}\label{fig:TEM_modes}
\end{figure*}

### 2018-08-15 Sections/optimising_the_world.tex

By defining an oracle\index{Oracle} that implements a polynomial-time algorithm on $n$ qubits, a Grover search over the input space of $O(2^n)$ configurations will determine the satisfying input to the oracle for a given desired output, which acts as the tagged element within the search algorithm. The Grover search yields a quadratic speedup for this search compared to a brute-force classical search, therefore requiring only $O(2^{n/2})$ oracle calls. While this is short of the exponential speedup one might hope for, a quadratic speedup can nonetheless be very significant for large problem instances, where even minor improvements could be of enormous value.

@@

Some problems in even harder classes than \textbf{NP}-complete can in some instances be \textit{approximated} using the same approach. The key to solving such problems is to define an oracle\index{Oracle} that attributes a \textit{score}\index{Score} to a given input, rather than a yes/no answer to perfect satisfiability, and answers `yes' or `no' depending on whether that score is above some defined threshold for approximation. As an illustrative example, consider the optimisation of, say, a complex traffic network, where the goal is to maximise flow through the network. Then we might define our score to be some flow metric for the network's graph.

>>>>

By defining an oracle\index{Oracles} that implements a polynomial-time algorithm on $n$ qubits, a Grover search over the input space of $O(2^n)$ configurations will determine the satisfying input to the oracle for a given desired output, which acts as the tagged element within the search algorithm. The Grover search yields a quadratic speedup for this search compared to a brute-force classical search, therefore requiring only $O(2^{n/2})$ oracle calls. While this is short of the exponential speedup one might hope for, a quadratic speedup can nonetheless be very significant for large problem instances, where even minor improvements could be of enormous value.

@@

Some problems in even harder classes than \textbf{NP}-complete can in some instances be \textit{approximated} using the same approach. The key to solving such problems is to define an oracle\index{Oracles} that attributes a \textit{score}\index{Score} to a given input, rather than a yes/no answer to perfect satisfiability, and answers `yes' or `no' depending on whether that score is above some defined threshold for approximation. As an illustrative example, consider the optimisation of, say, a complex traffic network, where the goal is to maximise flow through the network. Then we might define our score to be some flow metric for the network's graph.

### 2018-08-15 Sections/quantum_genetic_medicine.tex

Typically the end result is not a complete human genome from start to finish, but rather segments that capture regions of interest in the respective genome. In particular, certain genes or single-nucleotide polymorphisms (SNPs)\index{Single-nucleotide polymorphisms}\footnote{SNPs are positions in a genome whose nucleotides may differ between individuals within a species. Of course, the vast majority of the genetic makeup of individuals within a species is identical. Thus, the SNPs are sufficient to characterise the genetic differences between individuals and identify their genotype.} may be targeted as regions of interest during sequencing.

@@

The key goal is to properly simulate the interaction of candidate drug compounds\index{Drug compounds}, ligands\index{Ligands}, or functional groups\index{Functional groups} with biochemical processes at the molecular level. Classical techniques for such simulations include estimating electron densities using density functional theory\index{Electron density}\index{Density functional theory} (the potential energy surface)\index{Potential energy surface} of compounds, from which useful properties such as bonding affinities\index{Bonding affinity} may be determined.

@@

\subsection{Quantum drug trial simulations}\index{Quantum drug trial simulation}

@@

To achieve this, let us construct a classical algorithm for exhaustively constructing and enumerating organic drug molecules or functional groups, up to some cutoff size\index{Cutoff size}. The length of this list grows exponentially with the cutoff size. Next we implement this algorithm unitarily (which is always possible, writing the classical circuit as a reversible one), and construct it as a quantum oracle\index{Oracle} such that every input state (which acts as a pointer\index{Pointers} to an element in the list) yields as output a qubit representation\index{Qubit molecule representation} of the corresponding drug compound. Specifically, the oracle implements a transformation of the form,
\begin{align}
\hat{U}_\mathrm{oracle}\ket{i}_\mathrm{pointer}\ket{0}_\mathrm{drug}^{\otimes n} \to \ket{i}_\mathrm{pointer}\ket{\psi_i}_\mathrm{drug}^{(n)},
\end{align}
where $i$ is the index (pointer) to the drug element in the enumeration, and $n$ is the number of qubits encoding the representation of the drug molecule\footnote{This may be implemented unitarily, which is easy to see via its preservation of orthonormality.}.

@@

An R\&D organisation might specialise in the algorithmic generation\index{Algorithmic generation} (or hard-coding\index{Hard-coding}) of candidate drug compounds\index{Compounds}, which they would like to retain as a trade secret\index{Trade secrets}, but desire to license\index{Outsourced quantum computation} to third-party drug designers\index{Drug designers}, who wish to employ them in their computational pipeline\index{Quantum drug trial simulation}. The quantum search\index{Grover's algorithm} and Hamiltonian simulation\index{Quantum simulation} subroutines might similarly be outsourced or distributed over the cloud to vendors specialising in the implementation of these particular subroutines.

>>>>

Typically the end result is not a complete human genome from start to finish, but rather segments that capture regions of interest in the respective genome. In particular, certain genes or single-nucleotide polymorphisms (SNPs)\index{Single-nucleotide polymorphisms (SNPs)}\footnote{SNPs are positions in a genome whose nucleotides may differ between individuals within a species. Of course, the vast majority of the genetic makeup of individuals within a species is identical. Thus, the SNPs are sufficient to characterise the genetic differences between individuals and identify their genotype.} may be targeted as regions of interest during sequencing.

@@

The key goal is to properly simulate the interaction of candidate drug compounds\index{Drug compounds}, ligands\index{Ligands}, or functional groups\index{Functional groups} with biochemical processes at the molecular level. Classical techniques for such simulations include estimating electron densities using density functional theory\index{Electron density}\index{Density functional theory} (the potential energy surface)\index{Electron density} of compounds, from which useful properties such as bonding affinities\index{Bonding affinity} may be determined.

@@

\subsection{Quantum drug trial simulations}\index{Quantum drug trial simulations}

@@

To achieve this, let us construct a classical algorithm for exhaustively constructing and enumerating organic drug molecules or functional groups, up to some cutoff size\index{Cutoff size}. The length of this list grows exponentially with the cutoff size. Next we implement this algorithm unitarily (which is always possible, writing the classical circuit as a reversible one), and construct it as a quantum oracle\index{Oracles} such that every input state (which acts as a pointer\index{Pointers} to an element in the list) yields as output a qubit representation\index{Qubit molecule representation} of the corresponding drug compound. Specifically, the oracle implements a transformation of the form,
\begin{align}
\hat{U}_\mathrm{oracle}\ket{i}_\mathrm{pointer}\ket{0}_\mathrm{drug}^{\otimes n} \to \ket{i}_\mathrm{pointer}\ket{\psi_i}_\mathrm{drug}^{(n)},
\end{align}
where $i$ is the index (pointer) to the drug element in the enumeration, and $n$ is the number of qubits encoding the representation of the drug molecule\footnote{This may be implemented unitarily, which is easy to see via its preservation of orthonormality.}.

@@

An R\&D organisation might specialise in the algorithmic generation\index{Algorithmic generation} (or hard-coding\index{Hard-coding}) of candidate drug compounds\index{Compounds}, which they would like to retain as a trade secret\index{Trade secrets}, but desire to license\index{Outsourced quantum computation} to third-party drug designers\index{Drug designers}, who wish to employ them in their computational pipeline\index{Quantum drug trial simulations}. The quantum search\index{Grover's algorithm} and Hamiltonian simulation\index{Quantum simulation} subroutines might similarly be outsourced or distributed over the cloud to vendors specialising in the implementation of these particular subroutines.

### 2018-08-15 Sections/the_irrelevance_of_latency.tex

We see that the latency associated with entanglement distribution does not affect the latency of quantum state transmission when implemented via teleportation. The quantum network could continually be sharing entangled pairs between parties in a UDP-like\index{User datagram protocol} mode, who hold them in quantum memory. They ensure that Bell pairs are being distributed at a sufficient rate that parties have a buffer of entangled pairs sufficient to accommodate demand for future teleportations. This irrelevance of quantum latency is a uniquely quantum phenomena, not applicable to any classical protocols\footnote{One minor exception might be to treat randomness as a resource for randomised classical computation, i.e for application in \textbf{BPP} algorithms\index{BPP}. In that restricted instance the latency of our source of random bit-strings is also irrelevant since randomness is invariant under temporal displacement and can be buffered for future use.}.

>>>>

We see that the latency associated with entanglement distribution does not affect the latency of quantum state transmission when implemented via teleportation. The quantum network could continually be sharing entangled pairs between parties in a UDP-like\index{User Datagram Protocol (UDP)} mode, who hold them in quantum memory. They ensure that Bell pairs are being distributed at a sufficient rate that parties have a buffer of entangled pairs sufficient to accommodate demand for future teleportations. This irrelevance of quantum latency is a uniquely quantum phenomena, not applicable to any classical protocols\footnote{One minor exception might be to treat randomness as a resource for randomised classical computation, i.e for application in \textbf{BPP} algorithms\index{BPP}. In that restricted instance the latency of our source of random bit-strings is also irrelevant since randomness is invariant under temporal displacement and can be buffered for future use.}.
